\subject{Physics}

\short{Physics}{Indicate, by name or number, all of the following 4

conductors for which resistivity decreases when the temperature of the conductor is

increased:

1: copper wire

2: graphite

3: gallium-arsenide semiconductor

4: superconducting mercury



}
{2 AND 3}

\short{Physics}{A large metal rod 5 m long and 0.25 m2 in cross-sectional

area is subjected to a force of 200 N and is found to stretch .01 m. What is Young’s

modulus for this metal?



}
{4 x 105 Pa (ACCEPT: 400,000 Pa)}

\subject{Earth and Space}

\multiple{Earth and Space}{On which of the following days would an observerstanding directly on the Tropic of Capricorn view the Sun at his zenith at high noon?}
{vernal equinox}
{summer solstice}
{autumnal equinox}
{winter solstice}{Z) WINTER SOLSTICE}

\short{Earth and Space}{By name or number, name all of the following 4

absorption lines that are common in stars of the spectral class A:

1: hydrogen

2: ionized helium

3: calcium

4: nitrogen



}
{1 AND 3}

\subject{Biology}

\multiple{Biology}{Which of the following major classes of proteins involvedin DNA replication start the process of DNA unwinding by breaking a single DNAstrand, releasing the tension holding the helix in its supercoiled form?}
{helicases}
{primases}
{DNA ligases}
{topoisomerases}{Z) TOPOISOMERASES}

\short{Biology}{What mechanism of gene duplication typically arises by

crossover between unequally aligned chromatids, either on homologous chromosomes or

the same chromosome, and results in one chromosome with the straight-line duplication

of a sequence containing a gene and a sequence where the gene is lost?



}
{TANDEM GENE DUPLICATION}

\subject{Earth and Space}

\short{Earth and Space}{Indicate, by name or number, all of the following 3

statements which are attributes of barchan dunes:

1: they are the fastest moving of all dunes

2: they are widespread in the deserts of Central Asia

3: they have sand movement not only toward the slip face, but also around the edges of

the crescent



}
{1, 2, AND 3}

\multiple{Earth and Space}{Which of the following characteristics does NOTapply to loess, a wind-deposited silt formation?}
{Horizontally stratified}
{Fine-grained}
{Calcareous}
{Buff colored}{W) HORIZONTALLY STRATIFIED}

\subject{Chemistry}

\short{Chemistry}{Consider a mixture of acetone in chloroform. Indicate, by

name or number, all of the following 3 characteristics of negative azeotropes that can be

observed in this mixture:

1: positive change in enthalpy of mixing

2: higher vapor pressure than predicted from Raoult’s Law

3: higher boiling point than either pure acetone or pure chloroform



}
{3 ONLY}

\short{Chemistry}{Consider the reaction 2 NO(g) + O2(g) → 2 NO2(g).

When the concentration of NO is doubled, the rate of the reaction increases by a factor of

4. When both the O2 and the NO concentrations are doubled, the rate increases by a factor

of 8. What is the overall order of the reaction?



}
{3}

\subject{Math}

\short{Math}{Find the limit of the sequence whose nth term is

1

given by an  (1  )n .

n



}
{e}

\short{Math}{John’s parents have agreed to let John attend a

concert performed by his favorite band if he helps out around the house for an average 8

hours per week for 5 weeks. For the first 4 weeks, John spends 6, 13, 7, and 3 hours each

week. If he truly wants to attend his favorite band’s performance, how many hours should

he spend doing his chores during the fifth week?



}
{11}

\subject{Physics}

\short{Physics}{What property, implemented widely in Polaroids and other

polarizing filters, is the selective absorption of light where rays having varying

polarizations are absorbed in different amounts by the filter?



}
{DICHROISM}

\multiple{Physics}{A spaceship flies past Earth at a speed of 0.6c. If a crewmember onboard the spaceship measures its length to be 500 m, what is the observedlength of the spaceship from Earth?}
{300 m}
{320 m}
{400 m}
{440 m}{Y) 400 m}

\subject{Earth and Space}

\multiple{Earth and Space}{The cosmic background radiation that is observedtoday, with a temperature of roughly 2.7 K, consists of photons which werepredominantly active in which of the following time periods following the Big Bang?}
{singularity}
{recombination}
{dark age}
{reionization}{X) RECOMBINATION}

\multiple{Earth and Space}{The cosmological principle implies which of thefollowing conditions of the universe?}
{anisotropic and heterogeneous}
{anisotropic and homogeneous}
{isotropic and heterogeneous}
{isotropic and homogeneous}{Z) ISOTROPIC AND HOMOGENEOUS}

\subject{Biology}

\multiple{Biology}{T4, thyroxine, and T3, triiodothyronine, are two iodinecontaining amine hormones secreted by the follicles in the thyroid gland in the lower partof the neck. Persons with low peripheral deiodination can show signs of iodine deficiencyeven when they have high levels of T4. Which of the following differences between T4and T3 best accounts for this?}
{T4 is secreted in much larger amounts than T3}
{T4 is converted into T3 by enymes in cell plasma membranes}
{T4 has a longer half-life than T3}
{T4 is much less active than T3}{Z) T4 IS MUCH LESS ACTIVE THAN T3}

\multiple{Biology}{Which of the following components of the cell membrane,an example of which is a red blood cell, function primarily to determine the shape of thecell by forming supporting scaffold anchored to the membrane and cytoskeleton of thecell?}
{glycolipids}
{glycoproteins}
{spectrins}
{clathrins}{Y) SPECTRINS}

\subject{Earth and Space}

\short{Earth and Space}{By name or number, indicate all of the following 3

choices which is/are accurate conclusions from the Deep Sea Drilling Project, an

international program sponsored by several oceanographic institutions in order to gather

information about ocean basins and test processes that formed them:

1: sediment layers thicken with distance from the continental margins

2: youngest oceanic crust is adjacent to continental margins and increases in age towards

the ridge

3: sediment older than 180 million years does not exist in ocean basins



}
{3 ONLY}

\multiple{Earth and Space}{Which of the following plate boundaries is aconvergent plate boundary?}
{Antarctic and Pacific}
{South American and African}
{African and Arabian}
{Nazca and South American}{Z) NAZCA AND SOUTH AMERICAN}

\subject{Chemistry}

\short{Chemistry}{Consider an ionic solid such that the radius of the

smaller and larger ions are 50 pm and 150 pm, respectively. What is the likely structure

of this ionic solid?



}
{ZINC-BLENDE STRUCTURE}

\short{Chemistry}{Acrylonitrile, CH2CHCN, is used in the synthesis of

acrylic fibers. Beginning from the left, what is the hybridization on each carbon atom in

acrylonitrile?



}
{sp2, sp2, sp}

\subject{Math}

\short{Math}{Consider the sequence 3, 7, 11, 15…. What is the

10th term of this sequence?



}
{39}

\short{Math}{Simplify the following trigonometric expression

tan 2 x  1

completely:

1  cot 2 x



}
{tan 2 x}

\subject{Physics}

\multiple{Physics}{Which of the following statements is NOT true regardingdamped oscillations?}
{they are reductions in amplitude caused by dissipative forces}
{a system takes shorter time to return to equilibrium if it is overdamped}
{the mechanical energy during a damped oscillation decreases continuously andeventually reaches zero}
{if b, a constant describing the strength of the damping force, is less than the criticalvalue, the system oscillates with steadily decreasing amplitudeANSWER: X) A SYSTEM TAKES SHORTER TIME TO RETURN TO}{EQUILIBRIUM IF IT IS OVERDAMPED}

\multiple{Physics}{Your friend from Europe gifts you a 960-W toaster,designed to operate on a 240-V line. In order to use it with your USA-standard 120-V,which of the following transformers can you use to make some toast?}
{a step-up transformer with 4 times as many secondary coils than primary coils}
{a step-up transformer with 2 times as many secondary coils than primary coils}
{a step-down transformer with 4 times as many primary coils than secondary coils}
{a step-down transformer with 2 times as many primary coils than secondary coilsANSWER: X) A STEP-UP TRANSFORMER WITH 2 TIMES AS MANY}{SECONDARY COILS THAN PRIMARY COILS}

\subject{Earth and Space}

\multiple{Earth and Space}{Given that Deneb, a star in the constellation Cygnus,is a supergiant, in which of the following luminosity classes would it BEST be classified?}
{I}
{II}
{III}
{IV}{W) I}

\short{Earth and Space}{What infrared space telescope, launched in 2003 by

NASA, required cooling by liquid helium in order to function but continued to record

observations even after the cryogen was exhausted, and is thus now in the “warm phase”

of its mission?



}
{SPITZER SPACE TELESCOPE}

\subject{Biology}

\short{Biology}{In glycolysis, what enzyme phosphorylates fructose 6phosphate into fructose 1,6-bisphosphate?



}
{PHOSPHOFRUCTOKINASE}

\multiple{Biology}{Two parents are heterozygous for the recessive alleleproducing albinism. Which of the following best represents the probability that theparents will have one albino child among three children?}
{¼}
{¾}
{27/64}
{37/64}{Y) 27/64}

\subject{Earth and Space}

\short{Earth and Space}{What idea, which was consistent with Wegener’s

hypothesis concerning continental drift, was originally formulated to explain the

migration of magnetic poles through time, but now refers to the imaginary movement of

Earth’s magnetic poles relative to a continent fixed in position?



}
{APPARENT POLAR WANDERING (ACCEPT: POLAR WANDERING)}

\short{Earth and Space}{Order the following three magmatic compositions

in terms of increasing tendency to form pyroclastic flows: rhyolitic, basaltic, andesitic



}
{2, 3, 1}

\subject{Chemistry}

\multiple{Chemistry}{Of the following four oxoacids, which can bepredicted to have the lowest pKa value?}
{hypochlorous acid}
{chlorous acid}
{chloric acid}
{perchloric acid}{Z) PERCHLORIC ACID}

\short{Chemistry}{At constant temperature and pressure, order the

following 3 gases in terms of increasing mass density: N2, NH3, NO2



}
{2, 1, 3}

\subject{Physics}

\multiple{Physics}{Which of the following particles is NOT a product of thebeta-plus decay of a proton?}
{electron}
{positron}
{neutrino}
{neutron}{W) ELECTRON}

\short{Physics}{A Carnot engine takes in 3000 J of heat from a reservoir at

600 K, does some work, and discards heat to a reservoir at 480 K. How much work does

this Carnot engine do?



}
{600 JOULES}

\subject{Earth and Space}

\short{Earth and Space}{What explosion event marks the beginning of the triple

alpha process, and occurs when the density of the star’s core reaches 1 million g/cm3?



}
{HELIUM FLASH}

\short{Earth and Space}{Indicate, by name or number, all of the following 3

solar features that are thought to occur primarily in the photosphere, as opposed to other

layers of the sun:

1: granules

2: spicules

3: flares



}
{1 ONLY}

\subject{Biology}

\short{Biology}{What repeating structure, the smallest subunit of muscle

contraction, is bounded by discs of protein, or Z lines, and is composed of long, fibrous

proteins that slide past each other when muscles contract and relax?



}
{SARCOMERE}

\short{Biology}{Indicate, by name or number, all of the following 4 actions

that are isotonic contractions:

1: swinging a bat

2: holding a heavy ball in place at arm’s length

3: carrying a box

4: pushing against a stationary truck



}
{1 AND 3}

\subject{Earth and Space}

\multiple{Earth and Space}{Which of the following periods of geologic timesaw the adaptation of lobe-finned fish to terrestrial environments, eventually evolvinginto air-breathing amphibians?}
{Ordovician}
{Silurian}
{Devonian}
{Mississippian}{Y) DEVONIAN}

\short{Earth and Space}{Given the following 5 principal groups of climate

types, match them to the capital letters A, B, C, D, and E as classified by the Koppen

system of climate classification:

1: dry

2: humid middle-latitude, with mild winters

3: humid tropical

4: polar

5: humid middle latitude, with severe winters



}
{1: B; 2: C; 3: A; 4: E; 5: D}

\subject{Chemistry}

\short{Chemistry}{What phase of liquid crystals includes molecules that lie

parallel to one other and form sheets, resembling soldiers lining up on parade and

forming orderly layers?



}
{SMECTIC PHASE}

\short{Chemistry}{What volume of 6.0 M HNO3 would be needed to make

60 mL of 0.50 M solution?



}
{5 mL}

\subject{Math}

\short{Math}{Differentiate the following hyperbolic function:

d



sinh( x 2  3) 





dx



}
{2 x cosh( x2  3)}

\short{Math}{What is the product of the two smallest prime

factors of 250?



}
{10}

\subject{Physics}

\short{Physics}{What behavior, characteristic of permanent magnets, is

exhibited when a material magnetized to saturation while the external field is reduced to

zero has some remaining magnetization, and requires a magnetic field in the reverse

direction in order to reduce the magnetic field to zero?



}
{HYSTERESIS}

\short{Physics}{The maximum centripetal acceleration that your car can

sustain without skidding out of a curved path is 8 ms-2. If your car is traveling at a

constant 20 ms-1 on level ground, what is the radius of the tightest unbanked curve that

your car can travel?



}
{50 METERS}